---
title: "Brood Reducion Climwin"
author: "Ivan Bizberg"
date: "9/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.height = 10, fig.width = 15)
```


Libraries
```{r message=FALSE, warning=TRUE}
library(tidyverse)
library(lubridate)
# Analisis
library(climwin)
library(coxme)
library(survival)
library(survminer)
# Model selection
library(MuMIn)
library(bbmle)
# Plotting
library(ggthemes)
library(Greg)
library(rms)
```

Set path
```{r}
path = "conducta"
getwd()
```


Data
```{r}
# Biological data
BioData = read.csv(str_glue("ClimMultiFailCox.csv"), sep = ",", header = T) %>%
  select(WORKYEAR, NIDO, DATE, Time0, Time, Event, BroodReduction, HatchAsync, PROPORTIONALRANK) %>% 
  mutate(DATE = ymd(DATE))
```

```{r}
# Climatic data
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", 
                    header = T,stringsAsFactors = F) %>% 
  rename(Date = time) %>% mutate(Date = ymd(Date)) %>% mutate(SST = as.numeric(SST))
```

# Finding window for chlorophyll-a

```{r message=FALSE, warning=TRUE}
Bio = BioData %>% filter(DATE >= "2003-05-01") %>%
  na.omit()
```

```{r}
Clim = ClimData %>% select(Date , Chl) %>%
  filter(!Chl > 70) %>% # remove one oultlier
  na.omit()
```

##Climwin analysis

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Chl), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                         PROPORTIONALRANK + Event + strata(Event), data = Bio),
                      cinterval = "week",
                      range = c(17, 0),
                      type = "relative",
                      stat = c("min", "max", "mean", "sum"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); Comb
```
```{r}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r fig.height = 5, fig.width = 8, fig.align="center"}
plotdelta(dataset = Results)
```

#### Extract data Chl
```{r}
ClimVar = "Chl"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Chl),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync + PROPORTIONALRANK + Event + strata(Event), data = Bio),
                    cinterval = "week",
                    range = c(17, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 16)

plothist(Results, ClimWinRand)

```



# Data Bio 1989
```{r}
# Biological data
Bio = BioData %>% filter(WORKYEAR > "1989") %>%
  na.omit()
```

# Finding window for SST
```{r}
# Climatic data
Clim = ClimData %>% select(Date , SST) %>%
  na.omit()
```

##Climwin analysis

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$SST), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                         PROPORTIONALRANK + Event + strata(Event) , data = Bio),
                      cinterval = "week",
                      range = c(17, 0),
                      type = "relative",
                      stat = c("max", "min", "sum", "mean"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); Comb
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

#### Extract data SST
```{r}
ClimVar = "SST"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```

## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync + PROPORTIONALRANK + Event + strata(Event), data = Bio),
                    cinterval = "week",
                    range = c(17, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 29)

plothist(Results, ClimWinRand)

```



# Finding window for Rain and NRain

```{r}
# Climatic data
Clim = ClimData %>%
  select(Date , Rain, NdaysRain) %>%
  na.omit()
```

##Climwin analysis Rain

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Rain), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~
                                         HatchAsync +
                                         PROPORTIONALRANK + Event + strata(Event), data = Bio),
                      cinterval = "week",
                      range = c(22, 0),
                      type = "relative",
                      stat = c("mean", "sum"), # Error with max/quad and min/quad
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); Comb
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

#### Extract data Rain
```{r}
ClimVar = "Rain"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync + PROPORTIONALRANK + Event + strata(Event), data = Bio),
                    cinterval = "week",
                    range = c(22, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```


### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 29)

plothist(Results, ClimWinRand)

```


## Climwin analysis number of rainy days

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$NdaysRain), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                         PROPORTIONALRANK + Event + strata(Event) , data = Bio),
                      cinterval = "week",
                      range = c(22, 0),
                      type = "relative",
                      stat = c("mean", "sum"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); Comb
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```
#### Extract data NRain
```{r}
ClimVar = "NRain"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$NdaysRain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync + PROPORTIONALRANK + Event + strata(Event), data = Bio),
                    cinterval = "week",
                    range = c(22, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 29)

plothist(Results, ClimWinRand)

```



# Finding window for Wind

```{r}
# Climatic data
Clim = ClimData %>%
  select(Date , Wind) %>%
  na.omit()
```

##Climwin analysis Area_Rain
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Wind), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                         PROPORTIONALRANK + Event + strata(Event) , data = Bio),
                      cinterval = "week",
                      range = c(17, 0),
                      type = "relative",
                      stat = c("min", "max", "mean", "sum"),
                      func = c("lin", "quad"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); Comb
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

#### Extract data Wind
```{r}
ClimVar = "Wind"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Wind),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync + PROPORTIONALRANK + Event + strata(Event), data = Bio),
                    cinterval = "week",
                    range = c(17, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 29)

plothist(Results, ClimWinRand)

```

# Finding window for Area_Rain

```{r}
# Climatic data
Clim = ClimData %>%
  select(Date, Area_Rain, NdaysArea_Rain, NdaysArea_RainMedium) %>%
  na.omit()
```

##Climwin analysis 

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Area_Rain), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                         PROPORTIONALRANK + Event + strata(Event) , data = Bio),
                      cinterval = "week",
                      range = c(22, 0),
                      type = "relative",
                      stat = c("max","mean", "sum"), # Convergance with min
                      func = c("lin", "quad"), # Can't use log and inv because of zeros
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)); Comb
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```
#### Extract data Area_Rain
```{r}
ClimVar = "Area_Rain"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$Area_Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync + PROPORTIONALRANK + Event + strata(Event), data = Bio),
                    cinterval = "week",
                    range = c(22, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 29)

plothist(Results, ClimWinRand)

```


# Finding window for NArea_Rain

##Climwin analysis 

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$NdaysArea_RainMedium), # Climatic variable #NdaysArea_RainMedium
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                         PROPORTIONALRANK + Event + strata(Event) , data = Bio),
                      cinterval = "week",
                      range = c(26, 0),
                      type = "relative",
                      stat = c("mean", "max", "sum"), # Convergance with min
                      func = c("quad", "lin"), 
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)) ; Comb
```

```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
plotdelta(dataset = Results)
```

#### Extract data NArea_RainMedium
```{r}
ClimVar = "NArea_RainMedium"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 15,
                    xvar = list(ClimVar = Clim$NdaysArea_Rain),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync + PROPORTIONALRANK + Event + strata(Event), data = Bio),
                    cinterval = "week",
                    range = c(26, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "C", sample.size = 29)

plothist(Results, ClimWinRand)

```


# Compile new data
```{r, results="hide"}
Chl = read_csv("WinCoxChl.csv") %>% select(1:2, NIDO, WORKYEAR, Time) 
SST = read_csv("WinCoxSST.csv") %>% select(1:2, NIDO, WORKYEAR, Time) 
Rain = read_csv("WinCoxRain.csv") %>% select(1:2, NIDO, WORKYEAR, Time) 
NRain = read_csv("WinCoxNRain.csv") %>% select(1:2, NIDO, WORKYEAR, Time)
Wind = read_csv("WinCoxWind.csv") %>% select(1:2, NIDO, WORKYEAR, Time) 
Area_Rain = read_csv("WinCoxArea_Rain.csv") %>% select(1:2, NIDO, WORKYEAR, Time) 
NArea_RainMedium = read_csv("WinCoxNArea_RainMedium.csv") %>% select(1:2, NIDO, WORKYEAR, Time) 
```
```{r results="hide"}
Mother = read_csv("ClimMultiFailCox.csv")

FinalData = plyr::join_all(list(Mother, Chl, SST, Rain, NRain, Wind, Area_Rain, NArea_RainMedium), by = c("NIDO", "WORKYEAR", "Time"), type = "left") %>% glimpse()
write_csv(FinalData, "DATAClimMultiFailCox.csv")
```





# Which variable need to be refitted?
```{r}
FinalData = read_csv("DATAClimMultiFailCox.csv")
FinalData %>% glimpse()
CoxData = FinalData %>% 
  # filter(CONFIRMHEMB == T) %>%
  dplyr::mutate(across(c(PROPORTIONALRANK, HatchAsync, Chl, SST, Rain, NRain, Wind, Area_Rain,
                 AGEHEMB, AGEMACH, NArea_RainMedium), arm::rescale)) %>% 
  select(WORKYEAR, 
         # ANILLOMACH, AGEMACH, 
         # ANILLOHEMB, AGEHEMB,
         # CoupleExpLocal,
         PROPORTIONALRANK, HatchAsync, Chl, SST, Rain, NRain, Wind, 
         Area_Rain, NArea_RainMedium, Event, 
         Time0, Time, BroodReduction) %>% na.omit()

Coxme = coxme::coxme(Surv(Time0, Time, BroodReduction) ~
                       PROPORTIONALRANK + strata(Event) +
                       HatchAsync +
                       Chl +
                       I(Chl^2) +
                       SST +
                       I(SST^2) + 
                       Area_Rain +
                       I(Area_Rain^2) +
                       Wind +
                       I(Wind^2) +
                       # AGEHEMB + 
                       # I(AGEHEMB^2) + 
                       # CoupleExpLocal + 
                       # (1|ANILLOHEMB) +
                       (1|WORKYEAR),
                     data = CoxData)

summary(Coxme)
```
```{r}
# check_collinearity(Coxme)
rms::vif(Coxme)
```
We can see that cumulative and mean rain of number of rainy days have an effect on brood reduction probably because we are removing brood where both chicks died.
We also try using rain over all the area not only over the island and only the n of day of rain is significatif but weird windows 24-9. When i put number of day that the rain was greater than 1mm/day no significatif
We are now going to refit Chl, SST, Wind

Female and male  age (quad and lin) and couple experience has no effect on brood reduction



# Data For refitting
```{r, message=FALSE}
BioData = read_csv("DATAClimMultiFailCox.csv") %>% 
  select(PROPORTIONALRANK, HatchAsync, Chl, Chl_2, SST, SST_2, Event, BroodReduction, NIDO, WORKYEAR, DATE, Time0, Time)
```

```{r}
# Climatic data
ClimData = read.csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/ClimateVariables4.0.csv"), sep = ",", header = T,stringsAsFactors = F) %>% 
  rename(Date = time) %>% mutate(Date = ymd(Date))
```

# Reffiting Chlorophyll-a
```{r}
Bio = BioData %>% filter(DATE >= "2003-05-01") %>%
  na.omit() 
Bio %>% names()
```
 
```{r}
Clim = ClimData %>% select(Date , Chl) %>%
  filter(!Chl > 70) %>% # remove one oultlier
  mutate_at(vars(Chl), arm::rescale) %>% 
  na.omit()
```

##Climwin analysis

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$Chl), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                           PROPORTIONALRANK + Event + strata(Event) + SST_2, data = Bio),
                      cinterval = "week",
                      range = c(13, 0),
                      type = "relative",
                      stat = c("min", "max", "mean", "sum"),
                      func = c("quad", "lin"),
                      cmissing = "method1")
```

### Results

```{r}
Comb = (ClimWin$combos) %>% rownames_to_column() %>% arrange((DeltaAICc)) ; Comb
```


```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

### Weight
```{r, eval=TRUE}
dev.new(noRStudioGD = T)
weight <- weightwin(n = 2,
                    xvar = list(ClimVar = Clim$Chl),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = glm(BroodReduction ~ HatchAsync +
                                     PROPORTIONALRANK + 
                                     # Event + strata(Event) + 
                                     SST_2, data = Bio),
                    cinterval = "week",
                    range = c(12, 0),
                    type = "relative",
                    func = "quad",
                    weightfunc = "W",
                    par = c(3, 0.2, 0))
```



#### Extract data RefittedChl
```{r}
ClimVar = "RefittedChl"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 200,
                    xvar = list(ClimVar = Clim$Chl),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                           PROPORTIONALRANK + Event + strata(Event) + SST_2, data = Bio),
                    cinterval = "week",
                    range = c(13, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "AIC", sample.size = 16)

plothist(Results, ClimWinRand)

```


# Reffiting SST

```{r}
Clim = ClimData %>% select(Date , SST) %>%
  # mutate_at(vars(SST), arm::rescale) %>% 
  na.omit()
```

##Climwin analysis

```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimWin <- slidingwin(xvar = list(ClimVar = Clim$SST), # Climatic variable
                      cdate = Clim$Date,
                      bdate = Bio$DATE,
                      baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                           PROPORTIONALRANK + Event + strata(Event) + Chl_2, data = Bio), # we can see that there is a diference with Chl_2 and Chl
                      cinterval = "week",
                      range = c(8, 0),
                      type = "relative",
                      stat = c("min", "max", "sum", "mean"),
                      func = c("quad", "lin", "inv", "log"),
                      cmissing = "method1")
```

### Results

```{r}
Comb3 = (ClimWin$combos) %>% rownames_to_column() %>% 
  arrange((DeltaAICc)); Comb
```


```{r, fig.height = 5, fig.width = 8, fig.align="center"}
n = Comb %>% .[[1,1]] %>% as.numeric()
tidy_stat = Comb %>% .[[1, 5]] %>% as.character()
tidy_func = Comb %>% .[[1, 6]] %>% as.character()
Results = ClimWin[[n]]$Dataset ; head(Results, n = 4)
```
```{r}
plotdelta(dataset = Results)
```

### Weight
```{r, eval=FALSE}

dev.new(noRStudioGD = T)
weight <- weightwin(n = 2,
                    xvar = list(ClimVar = Clim$SST), # Climatic variable
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = glm(BroodReduction ~ HatchAsync +
                                       PROPORTIONALRANK + #Event + strata(Event) + 
                                     Chl_2, data = Bio),
                    cinterval = "week",
                    range = c(12, 0),
                    type = "relative",
                    func = "quad",
                    weightfunc = "W",
                    par = c(3, 0.2, 0))

```

#### Extract data RefittedSST
```{r}
ClimVar = "RefittedSST"
ClimateData = ClimWin[[n]]$BestModelData; head(ClimateData)
Area_RainData = ClimateData %>% select(contains("climate")) %>% rename(!!ClimVar := climate) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^2\\)")), ~ paste0(ClimVar, "_2")) %>% 
  rename_if((str_detect(names(.), "I\\(climate\\^3\\)")), ~ paste0(ClimVar, "_3")) %>% 
  bind_cols(Bio)
write_csv(Area_RainData, str_glue("WinCox{ClimVar}.csv"))
```
## Randomization
```{r message=FALSE, results="hide", cache=TRUE, warning=TRUE}
ClimRand <- randwin(repeats = 200,
                    xvar = list(ClimVar = Clim$SST),
                    cdate = Clim$Date,
                    bdate = Bio$DATE,
                    baseline = coxph(Surv(Time0, Time, BroodReduction) ~ HatchAsync +
                                           PROPORTIONALRANK + Event + strata(Event) + Chl_2, data = Bio),
                    cinterval = "week",
                    range = c(8, 0),
                    type = "relative",
                    stat = tidy_stat,
                    func = tidy_func,
                    cmissing = "method1")
```



### Results of randomization
```{r, fig.height = 5, fig.width = 8, fig.align="center"}
ClimWinRand = ClimRand[[1]]

# Diagnostic Plots

pvalue(Results, ClimWinRand, metric = "AIC", sample.size = 16)

plothist(Results, ClimWinRand)

```








# Final compilation of data
```{r, results='hide'}
# Compile new data
RefittedChl = read_csv("WinCoxRefittedChl.csv") %>% 
  select(1:2, NIDO, WORKYEAR, Time)
RefittedSST = read_csv("WinCoxRefittedSST.csv") %>% 
  select(1:2, NIDO, WORKYEAR, Time)

NewMother = read_csv("DATAClimMultiFailCox.csv")

FinalData = plyr::join_all(list(NewMother, RefittedChl, RefittedSST), by = c("NIDO", "WORKYEAR", "Time"), type = "left") %>% glimpse()
write_csv(FinalData, "RefittedDATAClimCox.csv")
```



# Final Result for brood reduction and climatic and enviromental factors
```{r}
FinalData = read_csv("RefittedDATAClimCox.csv")
FinalData %>% names()
CoxData = FinalData %>%  
  # filter(CONFIRMHEMB == T) %>%
  mutate_at(vars(RefittedSST, RefittedChl, AGEHEMB),
            arm::rescale) %>% 
  select(WORKYEAR, 
         ANILLOMACH, AGEMACH,
         ANILLOHEMB, AGEHEMB, CoupleExpLocal, Event, 
         PROPORTIONALRANK, HatchAsync, RefittedSST, RefittedChl, 
         Time0, Time, BroodReduction) %>% na.omit()

CoxmeWA = coxme(Surv(Time0, Time, BroodReduction) ~
                       PROPORTIONALRANK + strata(Event) +
                       HatchAsync +
                       RefittedChl +
                       I(RefittedChl^2) +
                       RefittedSST +
                       AGEHEMB + 
                       I(AGEHEMB^2) + 
                       AGEMACH + 
                       I(AGEMACH^2) + 
                       CoupleExpLocal + 
                       (1|WORKYEAR) ,
                       na.action = "na.fail",
                     data = CoxData)

  
summary(CoxmeWA)
```
```{r}
# check_collinearity(Coxme)
rms::vif(Coxme)
```







#### Call function TestRanef
```{r}
source(str_glue("C:/Users/{path}/Dropbox/PHD/Custom functions/TestRanef.R"))
```

## Select random effect
```{r}
Coxme0 = coxph(Surv(Time0, Time, BroodReduction) ~
                       PROPORTIONALRANK + strata(Event) +
                       HatchAsync +
                       RefittedChl +
                       I(RefittedChl^2) +
                       RefittedSST +
                       AGEHEMB + 
                       I(AGEHEMB^2) + 
                       CoupleExpLocal,
                       na.action = "na.fail",
                     data = CoxData)

# CoxmeA = update(CoxmeWA, . ~ . - (1|WORKYEAR))
# CoxmeW = update(CoxmeWA, . ~ . - (1|ANILLOHEMB))

anova(CoxmeWA, Coxme0)

TestRanef(Coxme0, CoxmeWA)
```

## Model Selection
```{r}
drg = dredge(CoxmeWA)
head(drg, n = 7)
delta2=get.models(drg,subset= delta < 2)
summary(model.avg(delta2))
```
```{r}
one=get.models(drg,subset= 1);one
```

# We need to add last reproductive effort from the mother 

```{r}
FemaleCosts = read_csv(str_glue("C:/Users/{path}/Dropbox/PHD/DATA/Csv/DATAFemaleCosts.csv")) %>% 
  select(ANILLOHEMB, WORKYEAR, NIDO, LastParentalCare_ALL, LastParentalCare_Egg, LastParentalCare_Chick)
RefitData = read_csv("RefittedDATAClimCox.csv")

AddData = left_join(RefitData, FemaleCosts, by = c("ANILLOHEMB", "WORKYEAR", "NIDO"))
write_csv(AddData, "FinalRefittedDATAClimCox.csv")
```


# Final Result for brood reduction and climatic and enviromental factors

### Females
```{r}
FinalData = read_csv("FinalRefittedDATAClimCox.csv")
FinalData %>% names()
CoxData = FinalData %>%  
  # filter(CONFIRMHEMB == T) %>%
  # filter(!ANILLOHEMB == "SA") %>%
  mutate_at(vars(RefittedSST, RefittedChl, AGEHEMB, PROPORTIONALRANK, HatchAsync, 
                 LastParentalCare_ALL, LastParentalCare_Egg, LastParentalCare_Chick),
            arm::rescale) %>% 
  select(WORKYEAR, 
         # ANILLOMACH, AGEMACH,
         # ANILLOHEMB, AGEHEMB,
         CoupleExpLocal, Event, NIDO,
         # LastParentalCare_ALL, LastParentalCare_Egg, LastParentalCare_Chick,
         PROPORTIONALRANK, HatchAsync, RefittedSST, RefittedChl, #RefittedWind,
         Time0, Time, BroodReduction) %>% na.omit()

CoxmeWA = coxme(Surv(Time0, Time, BroodReduction) ~
                  PROPORTIONALRANK + strata(Event) +
                  HatchAsync +
                  RefittedChl +
                  I(RefittedChl^2) +
                  # RefittedWind +
                  # I(RefittedWind^2) +
                  RefittedSST +
                  # AGEHEMB +
                  # I(AGEHEMB^2) +
                  # LastParentalCare_Chick +
                  # AGEMACH + 
                  # I(AGEMACH^2) + 
                  CoupleExpLocal +
                  (1|NIDO) + (1|WORKYEAR),
                na.action = "na.fail",
                data = CoxData)

  
summary(CoxmeWA)
```
```{r}
# check_collinearity(Coxme)
rms::vif(CoxmeWA)

```
## Select random effect
```{r}
Coxme0 = coxph(Surv(Time0, Time, BroodReduction) ~
                       PROPORTIONALRANK + strata(Event) +
                       HatchAsync +
                       RefittedChl +
                       I(RefittedChl^2) +
                       RefittedSST +
                       # AGEHEMB + 
                       # I(AGEHEMB^2) + 
                       CoupleExpLocal,
                       na.action = "na.fail",
                     data = CoxData)

# CoxmeA = update(CoxmeWA, . ~ . - (1|WORKYEAR))
# CoxmeW = update(CoxmeWA, . ~ . - (1|ANILLOHEMB))
```
```{r}
TestRanef(Coxme0, CoxmeWA)
```
```{r}
# TestRanef(Coxme0, CoxmeA)
```
```{r}
# TestRanef(Coxme0, CoxmeW)
```


## Model Selection
```{r}
drg = dredge(CoxmeWA)
head(drg, n = 7)
delta2=get.models(drg,subset= delta < 2)
summary(model.avg(delta2))
```
```{r}
one=get.models(drg,subset= 1);one
```

# Plotting
```{r}
FinalData = read_csv("FinalRefittedDATAClimCox.csv")
CoxData = FinalData %>%
  select(WORKYEAR,
         RefittedSST, RefittedChl, 
         Time0, Time, BroodReduction) %>% na.omit()
CoxBest = coxph(Surv(Time0, Time, BroodReduction) ~
                    RefittedChl +
                    I(RefittedChl^2) +
                    RefittedSST +
                    frailty(WORKYEAR),
                  data = CoxData)
```
```{r}
# SST
prs = predict(CoxBest, CoxData,
              type = c("risk"), se.fit = T)
NDpred = CoxData %>% mutate(pred = prs$fit)
NDpred %>%
  # filter(ClimWSST == median(ClimWSST)) %>%
  # filter(HatchAsync == median(HatchAsync)) %>%
  # filter(PROPORTIONALRANK == median(PROPORTIONALRANK)) %>%
  # filter(WORKYEAR == 2017) %>%
  # arrange(ClimWRain_2) %>%
  ggplot(aes(RefittedSST ,pred)) + geom_point() + geom_smooth(method = "lm", formula = y ~ x, size = 1) +
  # geom_smooth(stat = "identity", aes(ymin = lo, ymax = up)) +
  # scale_x_continuous(n.breaks = 20, limits = c(22,28)) +
  # scale_y_continuous(labels = scales::comma, n.breaks = 20, limits = c(0.1,10)) +
  geom_hline(yintercept = 1, size = 1.1, color = "red", linetype = "dashed") +
  geom_vline(xintercept = 24.5, size = 0.5, color = "red", linetype = "dashed") +
  labs(y = "Hazard Ratio") +
  theme_fivethirtyeight() + theme(axis.title = element_text())


# plotHR(CoxBest, term = "ClimWChl_2", plot.bty = "o", xlim = c(0, 30), xlab = "ClimWChl", se = T)
# sec = seq(from = 0, to = 29, by = 5)
```

```{r}
# Chl

NDpred %>%
  # filter(ClimWSST == median(ClimWSST)) %>%
  # filter(HatchAsync == median(HatchAsync)) %>%
  # filter(PROPORTIONALRANK == median(PROPORTIONALRANK)) %>%
  # filter(WORKYEAR == 2017) %>%
  # arrange(ClimWRain_2) %>%
  ggplot(aes(RefittedChl ,pred)) + geom_point() + geom_smooth() + #method = "lm", formula = y ~ x + I(x^2), size = 1) +
  # geom_smooth(stat = "identity", aes(ymin = lo, ymax = up)) +
  # scale_x_continuous(n.breaks = 20, limits = c(22,28)) +
  # scale_y_continuous(labels = scales::comma, n.breaks = 20, limits = c(0.1,10)) +
  geom_hline(yintercept = 1, size = 1.1, color = "red", linetype = "dashed") +
  geom_vline(xintercept = 1, size = 0.5, color = "red", linetype = "dashed") +
  labs(y = "Hazard Ratio") +
  theme_fivethirtyeight() + theme(axis.title = element_text())
  
# plotHR(CoxBest, term = "ClimWChl_2", plot.bty = "o", xlim = c(0, 30), xlab = "ClimWChl", se = T)
# sec = seq(from = 0, to = 29, by = 5)
```



